Matching bullets

### 2015-11-17 imaging-paper.Rnw
AFTE statements

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual. Roger Thompson's writeup on firearm identification cites AFTE 1992 procedures.\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}} }

>>>>

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual. Roger Thompson's writeup on firearm identification cites AFTE 1992 procedures.\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}} includes the following statements, both on page 34: `The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in ``sufficient agreement".' (my highlighting) and `Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows.'}
